\documentclass{ucbthesis}
\usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{babel}
\usepackage{biblatex}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsthm}
\NeedsTeXFormat{LaTeX2e}
\include{epigraph}

\usepackage{dsfont}
\usepackage{color}
\usepackage[bookmarks=false]{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\floatstyle{ruled}
\newfloat{algorithm}{tbp}{loa}
\providecommand{\algorithmname}{Algorithm}
\floatname{algorithm}{\protect\algorithmname}

\include{preamble}
\setlength{\epigraphwidth}{0.5\textwidth}

% Double spacing, if you want it.
% \def\dsp{\def\baselinestretch{2.0}\large\normalsize}
% \dsp

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

% \newtheorem{theorem}{Jibberish}

\bibliography{references}
\bibliography{path_inference}
\bibliography{socc}

\hyphenation{mar-gin-al-ia}

\begin{document}

% Declarations for Front Matter

\title{Large-scale, low-latency state estimation of cyberphysical systems, with an application to traffic estimation}
\author{Timothy Hunter}
\degreesemester{Spring}
\degreeyear{2014}
\degree{Doctor of Philosophy}
\chair{Professor Pieter Abbeel}
\othermembers{Professor Alexandre Bayen \\
  Professor Michael Franklin \\
  Professor Alexei Pozdnukhov}
\numberofmembers{4}
\prevdegrees{Dipl\^{o}me d'Ing\'{e}nieur (\'{E}cole Polytechnique) 2008 \\
  M.S. (Stanford University) 2009}
\field{Computer Sciences}
\campus{Berkeley}

% For a masters thesis, uncomment (remove the % at the beginning of)
% the following line.  This affects the title and approval pages,
% which by default calls this a "dissertation", not a "thesis".

%\itsamasters

% The title page generated by LaTeX is now acceptable for handing in.
% (This was not always the case).

\maketitle
\approvalpage
\copyrightpage

% \include{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
\begin{center}
To Ossie Bernosky\\\vspace{12pt}
\end{center}
\vfil\null
\end{dedication}

\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables

\begin{acknowledgements}
\input{acks}
\end{acknowledgements}

\end{frontmatter}

\pagestyle{headings}

\include{intro}

\chapter{A map-matching algorithm for GPS data}
\epigraph{Pourquoi donc, reprit le Sirien, citez-vous un certain Aristote en grec?
C'est, r\'{e}pliqua le savant, qu'il faut bien citer ce qu'on ne comprend point
du tout dans la langue qu'on entend le moins.}{Voltaire \emph{in} Micromegas}
% \epigraph{Le faux se r\'{e}pand vite, et le vrai surnage lentement.}{George Sand, \emph{in} C\'{e}sarine Dietrich}
\include{pif_1intro}
\include{pif_2pathdiscovery}
\include{pif_3model}
\include{pif_4training}
\include{pif_5experiments}
\include{pif_6conclusion}

\chapter{A large-scale distributed streaming model}
\epigraph{A lawyer without history or literature is a mechanic, a mere working mason;
if he possesses some knowledge of these, he may venture to call himself an architect.}{Sir Walter Scott, in Guy Mannering}
\include{socc_1intro}
\include{socc_2model}
\include{socc_3model_gamma}
\include{socc_4dstreams}
\epigraph{Mais on ne se bat pas dans l espoir du succes! Non! non! c'est bien plus beau lorsque c'est inutile!}{Cyrano de Bergerac}
\include{socc_5experiments}
\include{socc_6conclusion}

% \appendix
% \chapter{More Monticello Candidates}

% \include{gmrf}

\chapter{Large scale something}
\epigraph{
Crombile maintenant ne venait plus au conseil; lev\'{e} \`{a} cinq heures du matin, 
il travaillait dix-huit heures \`{a} son bureau et tombait epuis\'{e} dans 
sa corbeille o\`{u} les huissiers 
le ramassaient avec les papiers qu'ils allaient vendre 
aux attach\'{e}s militaires de l'empire voisin.
}{Anatole France, \emph{in} L'\^{i}le des pingouins}
\include{kdd_1introduction}
\include{kdd_2stop-and-go}
\include{kdd_3graph-model}
\include{kdd_4inference}
\include{kdd_5evaluation}
\include{kdd_6conclusion}

\chapter{Conclusion}
\epigraph{He attacked everything in life with a mixture of extraordinary genius and naive incompetence
and it was often difficult to tell which was which.}{Douglas Adams, in The Hitchhiker s guide to the galaxy}

\printbibliography

\end{document}
